Creating a Testing Framework and Workflow for Developers New to Web Application Engineering

### 2014-06-14 Paper/paper.tex
Tougher Edits, Is it done?

@@

>>>>

\subsection{Choosing Tools}
In order to find suitable tools, we wanted to take several approaches. First, we looked at existing research paper in the domain of web application testing and selected tools that were mentioned that still had active projects. We looked at the related works sections of those papers and chose tools from related papers as well. We then looked at major web applications like jQuery, LinkedIn, Twitter, and Facebook to what tools they were using and found a few tools that way. We looked at a number of projects that were internal and external to Google that were discussed at Google I/O 2013. Finally, we searched online for the latest open-source tools that may be in beta or new to the testing scene.

@@

\section{Test Metrics}
Below are several tables of metrics we collected after completing our tests. The tables are: Lines of Code, Code Coverage, Separate Tests, Asserts, and Mock Objects and Functions.

The Lines of Code table measures how many lines of test code were written per line of source code. The Code Coverage table shows the coverage statistics for our tests including statement, branch, function, and line coverage. The Separate Tests table shows how many tests were written for each part of the Authoring tool we tested. The Asserts table breaks down the tests even further into how many asserts were written for each part of the Authoring tool. Finally, the Mock Objects and Functions table shows how many mock objects and stubbed functions we had to create to ensure proper Unit Testing of the Controller and Server modules. The Model was self-contained enough that we did not need to create mock objects or functions for it.

% Test LOC vs Production LOC
% peDesignerModel
% T: 104 
% S: 93

% peDesignerController
% T: 438 
% S: 862

% peDesignerServer
% T: 206 
% S: 321

% UI:
% DesignerMain: 16
% Event: 140
% Chapter: 133
% Story: 102
% Cleanup: 46

\FloatBarrier
\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|l|}
\hline
                & Source LOC & Test LOC & Test LOC per Source LOC \\ \hline
Unit Tests      &          &       &                     \\ \hline
Model      & 93         & 104      & 1.11                    \\ \hline
Controller & 862        & 438      & 0.51                    \\ \hline
Server     & 321        & 206      & 0.64                    \\ \hline
UI Tests      &         &      &                     \\ \hline
Main          & N/A*       & 16       & N/A*                    \\ \hline
Event         & N/A*       & 140      & N/A*                    \\ \hline
Chapter       & N/A*       & 133      & N/A*                    \\ \hline
Story         & N/A*       & 102      & N/A*                    \\ \hline
Cleanup**    & N/A*       & 46       & N/A*                    \\ \hline
\end{tabular}
\captionof{table}{Lines of Code}
\end{table}
\FloatBarrier

\footnotesize
* The source for the UI is dynamic based and so no measurement is possible.

** Though not direct testing, the Cleanup code was important to bring the application back to its starting state.
\normalsize

% Test coverage
% Statement: 98.78\% 565 / 572
% Branch: 50\% 4/8
% Function: 96\% 120/125
% Line: 98.77\% 564/571

\FloatBarrier
\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
          & Coverage & Elements Covered / Total Elements \\ \hline
Statement & 98.78\%  & 565 / 572                         \\ \hline
Branch    & 50\%*     & 4 / 8                             \\ \hline
Function  & 96\%     & 120 / 125                         \\ \hline
Line      & 98.77\%  & 564 / 571                                  \\ \hline
\end{tabular}
\captionof{table}{Code Coverage}
\end{table}
\FloatBarrier

\footnotesize
* Branches not covered were diagnostic in nature.
\normalsize

% # Tests
% Unit: 50
% peDesignerModel: 15
% peDesignerController: 23
% peDesignerServer: 12

% UI: 29
% Main: 1
% Event: 9
% Chapter: 9
% Story: 7
% Cleanup: 3

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
     &            & Tests \\ \hline
Unit Tests &            & 50          \\ \hline
     & Model      & 15          \\ \hline
     & Controller & 23          \\ \hline
     & Server     & 12          \\ \hline
UI Tests   &            & 29          \\ \hline
     & Main       & 1           \\ \hline
     & Event      & 9           \\ \hline
     & Chapter    & 9           \\ \hline
     & Story      & 7           \\ \hline
     & Cleanup    & 3           \\ \hline
\end{tabular}
\captionof{table}{Separate Tests}
\end{table}

% # Asserts
% Unit: 237
% peDesignerModel: 33
% peDesignerController: 128
% peDesignerServer: 76

% UI: 43
% Main: 5
% Event: 13
% Chapter: 13
% Story: 12
% Cleanup: 0

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
           &                 & Asserts \\ \hline
Unit Tests &                 & 237     \\ \hline
           & Model      & 33      \\ \hline
           & Controller & 128     \\ \hline
           & Server     & 76      \\ \hline
UI Tests   &                 & 43      \\ \hline
           & Main         & 5       \\ \hline
           & Event        & 13      \\ \hline
           & Chapter      & 13      \\ \hline
           & Story        & 12      \\ \hline
           & Cleanup      & 0       \\ \hline
\end{tabular}
\captionof{table}{Asserts}
\end{table}

% # Mock objects
% peDesignerController:
%   Objects: 13
%   Functions: 32

% peDesignerServer:
%   Objects: 4
%   Functions: 11

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
                     & Mock Objects & Mock Functions \\ \hline
Controller Unit Test & 13           & 32              \\ \hline
Server Unit Test     & 4            & 11              \\ \hline
\end{tabular}
\captionof{table}{Mock Objects and Functions}
\end{table}

% Bugs Uncovered
